An Open-Source Implementation of the CMPS Algorithm for Assessing  Similarity of Bullets

### 2021-08-05 CMPSpaper_writing/CMPSpaper_writing.Rmd
to do list :)

>>>>

\hh{Still to add: the CMPS diff measure, in which you subtract the background. 
A comparison to results from bulletxtrctr's random forest.}
\hh{The random forest is spitting out results on a [0-1] interval - so we might need to compare to the adjusted measure. That comarison should go into a separate section just before the discussion. Like - comparison to other existing methods ... special request from Alicia :)}
